Prospects of detecting gamma-ray emission from galaxy clusters: cosmic rays and dark matter annihilations

### 2011-04-10 paper.tex
figures+text

@@

Our goal in this section is to derive a simple spatial model for the
distribution of SD in galaxy clusters. For this reason we use stacked cluster
observations by Sloan in the $r$-band that trace the stars. We assume that the
dust trace the stars in the clusters, which should be accurate to the order of
magnitude estimate that we are interested in here. The stacked surface
brightness profiles in \cite{2005MNRAS.358..949Z} are measured at redshift $z
\sim 0.25$ with an average mass of the clusters of
$4.0\times10^{13}\,\msun$. The profiles are build up out of three components;
diffuse intracluster light (ICL), galaxies, and the brightest cluster galaxy
(BCG) in the center of clusters. However, the total volume overlap of the ISM to
the cluster is very small compared to the ICL- and BCG overlap with the cluster,
thus the relative contribution of the galaxies to the IC emission is
suppressed. To remove this bias we cut out the galaxies that have been smoothed
over the cluster in the stacked analysis. In Fig.~\ref{fig:SD_spatial} we show
the SDSS stacked brightness profiles as well as the fitted profiles\footnote{The
  measured brightness is converted into units of $\rmn{erg}\,\rmn{s}^{-1}$ using
  \cite{2010...book} $S(\rmn{mag}\,''^{-2}) =
  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$, where
  the sun's absolute magnitude in the $r$-band is given by
  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the luminosity of the
  sun by $L_\odot=3.85\,10^{33} \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the
unitless $\rvir$ normalized area to resembele the expected luminosity at radius
$r$. Our benchmark spatial model is shown with the solid black line, and include
the contribution from the ICL and BCG.

Instead of modelling the surface brightness with a de Vaucouleur
profile with the addition of a power-law, we use a double beta profile
model for simplicity of deprojection given by:
\begin{equation}
S_\sd (r_\bot)= \sum_{i=1}^2 \,S_i\, 
\left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
^{-3\beta_i + 1/2}\,,
\label{double_beta}
\end{equation}
where we found the following best fitted central brightness ($S_i$),
core radius ($r_{\mathrm{c}_i}$), and slope ($\beta_i$):
\begin{eqnarray}
 S_1&=&5.0\times10^{-6}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
r_{\mathrm{c}_1}=130\,\rmn{kpc},\,
\beta_1=0.54\nonumber\\
 S_2&=&3.9\times10^{-3}\,\rmn{erg}\,\rmn{cm}^{-2}\,\rmn{s}^{-1},\,
r_{\mathrm{c}_2}=2.8\,\rmn{kpc},\,
\beta_2=0.53\,.\nonumber\\
\label{fit_spatial_IR}
\end{eqnarray}
The 3D spatial profile is derived by deprojecting the surface
brightness in Eq.~(\ref{double_beta}) (see
e.g. \cite{2004A&A...413...17P} for details about the deprojection):
\begin{eqnarray}
  j(r)  = \sum_{i=1}^2 \frac{S_i}{2\pi\,r_{\mathrm{c}_i}}\,
  \frac{6 \beta_i - 1}{\left(1 + r^2/r^2_{\mathrm{c}_i}\right)^{3\beta_i}}\,
  \mathcal{B}\left(\frac{1}{2},3\beta_i\right)\,,
\end{eqnarray}
where $\mathcal{B}(a,b)$ denotes the beta-function
\cite{1965hmfw.book.....A}.

Our goal in this section is to derive a simple spectral model for SD in galaxy
clusters. Since the radiation from galaxies are expected to leak out into the
ICM, we expect similar spectral distributions, at least to the order of
magnitude that we are interested in here. Hence, we use the IR to UV spectrum
derived in \cite{2006ApJ...648L..29P} for a MW type galaxy to characterize the
spectral distribution of light from SD in a cluster. Note, however, that we only
keep the spectral shape, and renormalize the spectral distribution using the
luminosity from SD.

In Fig.~\ref{fig:SD_spectra} we show the spectral distribution of the
light from SD together with the CMB black-body distribution in a
galaxy cluster, both at the radius $r=0.071\rvir$ where the energy
density of the smooth light from SD (see Fig.~\ref{fig:SD_Edens})
equals the energy density of the CMB. We have renormalized both the
spectral data and the fitted spectra using the luminosity from stars
and dust individually (see the normalization section below for further
details).

We choose to fit the spectrum of the dust that peaks at about
$10^{-2}\,\ev$ with a double power-law, and the slightly wider
spectral distribution of the stars that peaks at about $1\,\ev$ with a
tipple power-law. We find the best fit spectra for the SD in a
cluster through:
\begin{eqnarray}
  \eph^2\frac{\dd^2 N_\ph}{\dd \eph \dd V}
  &\equiv& u_\sd(\eph) =  \sum_i N_i(\lx) u_i^\gal(\eph)\,,\nonumber \\ 
\rmn{where}\quad i&=&\{\rmn{stars,dust}\} \qquad \rmn{and}\\ 
% &=&  N_\dust(\lx) u_\dust^\gal(\eph) + N_\stars(\lx) u_\stars^\gal(\eph)  \nonumber \\ 
%  \\
  u_\stars^\gal(\eph) &=& \frac{23\,\rmn{eV}}{\rmn{cm}^3} 
  \left(\frac{1.23\,\rmn{eV}}{\eph}\right)^{1.9} \nonumber \\
  &\times&\left[1+\left(\frac{2.04\,\rmn{eV}}{\eph}\right)^{20}\right]
  ^{-\frac{1.9}{20}}\nonumber \\
  &\times& \left[1+\left(\frac{0.78\,\rmn{eV}}{\eph}\right)^{20}\right]^{-\frac{2.6}{20}}\,, \\
  u_\dust^\gal(\eph) &=& 
  \frac{40\,\rmn{eV}}{\rmn{cm}^3} 
  \left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{4.9}\nonumber \\
  &\times& \left[1+\left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{1.9}\right]^{-4.9}\,.
\end{eqnarray}

The spatial and spectral distribution functions
of the light from SD in a cluster are both normalized with a constant
determined from the luminosity in each respective wavelength. The
specific energy density is given by
\begin{eqnarray} 
u_\sd(\eph, r) &=& \frac{j(r)}{j(0)}\,u_\sd(\eph) \nonumber\\
&=& \frac{j(r)}{j(0)}\,\sum_i N_i(\lx) u_i^\gal(\eph)\,,
\end{eqnarray}
where we fix the unitless normalization $N_i(\lx)$ using the total
energy of the light in SD  within $\rvir$:
\begin{eqnarray} 
  E_{i,\vir} &=& L_i \frac{\rvir}{c} \nonumber \\
  &=&N_i(\lx)\int_{\rvir} \int_i \,\frac{j(r)}{j(0)} 
  \frac{u_i^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
 \rmn{for}\quad i&=&\{\rmn{stars,dust}\}\,.
\label{eq:E_SD}
\end{eqnarray}
Here we approximate the total energy of the photons within $\rvir$
($E_{i,\vir}$) with the luminosity $L_i$ \cite{2008A&A...490..547G}
times the typical timescale it takes for a photon to propagate through
the cluster (we assume that the cluster is optically thin). Once we
derived the SD luminosities for a well representative cluster, we use
a IR to X-ray scaling relation to estimate the luminosity from an
arbitrary cluster:
\begin{equation}
L_\ir=1.05\times10^{45}\,\rmn{erg\,s}^{-1}\,
\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,,
\label{eq:SD-X}
\end{equation}
where $\lx$ is the luminosity of the X-ray emitting gas within
$\rvir$.

The normalization constant for the starlight $N_\stars(\lx)$ is derived
in the following three steps: (1) We use the average apparent magnitude
in the $(r+i)$-band $m_{(r+i),0.25}\approx 15.5$
\cite{2005MNRAS.358..949Z} of a cluster with the average mass
$\mvir=4.0\times10^{13}\msun$ at a redshift $z=0.25$ to derive the
luminosity from the stars:
\begin{equation}
L_\stars=10^{\frac{m_\odot-m_{(r+i),0.25}}{2.5}}
\left(\frac{D_\clu}{D_\odot}\right)^2 L_\odot
\approx 7.1\times10^{44}\,\rmn{erg}\,\rmn{s}^{-1}\,,
\label{eq:L_star}
\end{equation}
where the apparent magnitude of the sun $m_\odot\approx -27.1$, the
distance to the sun $D_\odot=4.85\times10^{-6}\,\rmn{pc}$, the
luminosity of the sun $L_\odot=3.85\times10^{33}\,\rmn{erg\,s}^{-1}$,
and the distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. (2)
We use the IR to X-ray scaling relation in Eq.~(\ref{eq:SD-X}) to derive
a more general form of the luminosity from stars in
Eq.~(\ref{eq:L_star}) that is valid for an arbitrary cluster mass. The
cluster X-ray luminosities are found in the extended HIFLUGCS
catalogue \cite{2002ApJ...567..716R} to which we have added the Virgo
cluster. (3) The normalization constant for the stars is
determined from the above steps together with Eq.~(\ref{eq:E_SD})
where we integrate over the cluster volume and spectral distribution
of the stars. It is given by
\begin{equation}
 N_\stars(\lx) = 1.2\times10^{-9}\,
\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
\label{eq:N_stars}
\end{equation}
Note that since the luminosities include the contribution from
galaxies, we have integrated the spatial distribution including
galaxies to derive the normalization. Once the normalization is fixed,
the SD energy densities are derived from the spatial distribution
where galaxies have been excluded.

The normalization constant for the dust $N_\dust(\lx)$ is derived in the
following four steps: (1) We use a cluster with the the average mass
$\mvir=4.0\times10^{13}\msun$ and estimate the X-ray luminosity from
the X-ray to mass scaling relations derived for the Representative
XMM-Newton Cluster Structure Survey (REXCESS) in
\cite{2009A&A...498..361P}:
\begin{equation}
\lx=1.18\times 10^{44}\,\rmn{erg\,s}^{-1}
\left(\frac{M_{200}}{10^{14}\msun}\right)^{1.81}\,,
\end{equation}
where we have used that $M_\rmn{200} \approx 1.58\,M_\rmn{500}$ for a
small cluster \footnote{We derive the factor 1.58 using
  $M_\rmn{200}/M_\rmn{500}$ for the clusters in the HIFLUGCS catalogue
  with a mass similar to $\mvir=4.0\times10^{13}\msun$ that we use to
  derive the luminosity from dust.}. (2) From the IR to X-ray scaling
relation in Eq.~(\ref{eq:SD-X}) we can now estimate calculate the
luminosity from the dust for a $\mvir=4.0\times10^{13}\msun$ cluster;
$L_\dust=4.7\times10^{44}\,\rmn{erg\,s}^{-1}$. (3) We generalize
Eq.~(\ref{eq:L_star}) to an arbitrary cluster mass using
Eq.~(\ref{eq:SD-X}) together with the cluster X-ray luminosities in
the extended HIFLUGCS catalogue. (4) The normalization constant for
the dust can now be determined from from the above steps together with
Eq.~(\ref{eq:E_SD}) where we integrate over the cluster volume and
spectral distribution of the dust. It is given by
\begin{equation}
 N_\dust(\lx) = 1.4\times10^{-9}\,
\left(\frac{\lx}{10^{44}\rmn{erg\,s}^{-1}}\right)^{0.53}\,.
\label{eq:N_dust}
\end{equation}
Note that since the luminosities include the contribution from
galaxies, we have integrated the spatial distribution including
galaxies to derive the normalization. Once the normalization is fixed,
the SD energy densities are derived from the spatial distribution
where galaxies have been excluded.

The spatial distribution of the SD energy density is an important quantity since
it impacts the steady state electron and positron spectra through cooling. A
higher density of SD in a cluster suppresses the spectra of the upscattering
particles. With the formalism presented above, we can now derive the energy
density from starlight and dust in a galaxy cluster through
\begin{eqnarray}
\label{eq:U_SD}
u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
=\int \dd \eph \frac{u_\sd(\eph, r)}{\eph}
\nonumber \\
&=&  \frac{j(r)}{j(0)}  \int \dd \eph \sum_i 
N_i(\lx) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
\end{eqnarray}
In Fig.~\ref{fig:SD_Edens} we compare the energy densities from
different radiation fields in a galaxy cluster with the mass
$\mvir=4.0\times10^{13}\msun$. We use two different profiles for the
SD energy density, where the total profile includes the contribution
from the ICL, the BCG and all the galaxies, while the galaxies are
excluded in the smooth profile. We find that even for a cluster with a
relative small mass the energy density of the SD components dominates
over the CMB and the magnetic fields (with a central B field of 3~$\mu
G$) within about 10\% of $\rvir$. Outside this radius the CMB is
dominating the energy density of the cluster, hence the magnetic
fields are always subdominant in the cluster and can safely be removed
from cluster IC calculations for a reasonable central B-field and
spectral index. Note that in this work we keep the contribution
from B-fields to the total energy density for consistency.

>>>>

Our goal in this section is to derive a simple spectral model for SD
in galaxy clusters. The SD light from clusters is dominated by the
emission from galaxies. This radiation is expected to leak out into
the much larger volume of the ICM, hence we approximate the spectral
distribution of the ICL with the light from galaxies. We use the far
infrared to ultraviolet spectrum derived in \cite{2006ApJ...648L..29P}
for a MW type galaxy to characterize the SD spectral distribution of a
cluster. Note that we only keep the spectral shape, and renormalize
the spectral distribution using the luminosity from SD.

In Fig.~\ref{fig:SD_spectra} we show the spectral distribution of the
light from SD together with the CMB black-body distribution in a
galaxy cluster, both at the radius $r=0.02\rvir$ where the energy
density of the smooth light from SD (see Fig.~\ref{fig:SD_Edens})
equals the energy density of the CMB. We have renormalized both the
spectral data and the fitted spectra using the luminosity from stars
and dust individually.

We choose to fit the spectrum of the dust that peaks at about
$10^{-2}\,\ev$ with a double power-law, and the slightly wider
spectral distribution of the stars that peaks at about $1\,\ev$ with a
tipple power-law. We find the best fit spectra for the SD in a
cluster through:
\begin{eqnarray}
  \eph^2\frac{\dd^2 N_\ph}{\dd \eph \dd V}
  &\equiv& u_\sd(\eph) =  \sum_i N_i(\mvir) u_i^\gal(\eph)\,,\nonumber \\ 
\rmn{where}\quad i&=&\{\rmn{stars,dust}\} \qquad \rmn{and}\\ 
% &=&  N_\dust(\lx) u_\dust^\gal(\eph) + N_\stars(\lx) u_\stars^\gal(\eph)  \nonumber \\ 
%  \\
  u_\stars^\gal(\eph) &=& \frac{23\,\rmn{eV}}{\rmn{cm}^3} 
  \left(\frac{1.23\,\rmn{eV}}{\eph}\right)^{1.9} \nonumber \\
  &\times&\left[1+\left(\frac{2.04\,\rmn{eV}}{\eph}\right)^{20}\right]
  ^{-\frac{1.9}{20}}\nonumber \\
  &\times& \left[1+\left(\frac{0.78\,\rmn{eV}}{\eph}\right)^{20}\right]^{-\frac{2.6}{20}}\,, \\
  u_\dust^\gal(\eph) &=& 
  \frac{40\,\rmn{eV}}{\rmn{cm}^3} 
  \left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{4.9}\nonumber \\
  &\times& \left[1+\left(\frac{0.0144\,\rmn{eV}}{\eph}\right)^{1.9}\right]^{-4.9}\,.
\end{eqnarray}

The spatial and spectral distribution functions of the light from SD
in a cluster are both normalized with a mass dependent function
determined from the luminosity in each respective wavelength band. The
specific energy density is given by
\begin{eqnarray} 
u_\sd(\eph, r) &=& j(r)\,u_\sd(\eph) \nonumber\\
&=& j(r)\,\sum_i N_i(\mvir) u_i^\gal(\eph)\,,
\end{eqnarray}
where $j(r)$ describes the spatial distribution. We fix the unitless
normalization $N_i(\mvir)$ using the total energy of the light in SD
within $\rvir$:
\begin{eqnarray} 
  E_{i,\vir} &=& L_i \frac{\rvir}{c} \nonumber \\
  &=&N_i(\mvir)\int_{\rvir} \int_i \,j(r) 
  \frac{u_i^\gal(\eph)}{\eph}\,\dd V\dd \eph\,,\nonumber \\
 \rmn{for}\quad i&=&\{\rmn{stars,dust}\}\,.
\label{eq:E_SD}
\end{eqnarray}
Here we approximate the total energy of the photons within $\rvir$
($E_{i,\vir}$) with the luminosity $L_i$ \cite{2008A&A...490..547G}
times the typical timescale it takes for a photon to propagate through
the cluster (we assume that the cluster is optically thin). We derive
the luminostity from the stars using
\begin{eqnarray}
L_\stars(M_{200\rmn{av}})&=&10^{\frac{m_\odot-m_\rmn{cl}-2.5\log\left(1+z\right)}{2.5}}
\left(\frac{D_\clu}{D_\odot}\right)^2 L_\odot\nonumber\\
&\approx& 5.3\times10^{44}\,\rmn{erg}\,\rmn{s}^{-1}\,,
\label{eq:L_star}
\end{eqnarray}
where the average apparent magnitude of a cluster at $z\approx 0.25$
in the $(r+i)$-band is given by $m_\rmn{cl}\approx 15.5$
\cite{2005MNRAS.358..949Z}. This magnitude is derived from stacking
clusters observed by the SDSS with the average mass
$M_{200\rmn{av}}=4.0\times10^{13}\msun$ and redshift close to
$z=0.25$. We also use an apparent magnitude of the sun $m_\odot\approx
-27.7$, distance to the sun $D_\odot=4.85\times10^{-6}\,\rmn{pc}$,
luminosity of the sun $L_\odot=1.17\times10^{33}\,\rmn{erg\,s}^{-1}$,
and distance to the cluster $D_\clu=1.26\times10^9\,\rmn{pc}$. To
account for different cluster masses in our analisys we adopt a simple
mass scaling of the luminosity from the stars in clusters. Since a
large contribution of the total starlight in a cluster comes from the
brightest central galaxy (BCG), we assume that the total starlight has
the same halo mass scaling as the BCG \cite{2010ApJ...713.1037H}
\begin{equation}
L_\stars(\mvir)=L_\stars(M_{200\rmn{av}})\,
\left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,.
\end{equation} 
We can now fix the normalization constant for the stars in
Eq.~(\ref{eq:E_SD}) by integrating over the cluster volume and
spectral distribution of the stars. It is given by
\begin{equation}
 N_\stars(\mvir) = 2.1\times10^{33}\,
\left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,
\frac{\rvir}{\int_{\rvir} j(r) \,\dd V}\,.
\label{eq:N_stars}
\end{equation}
\del{Note that since the luminosities include the contribution from
galaxies, we have integrated the spatial distribution including
galaxies to derive the normalization. Once the normalization is fixed,
the SD energy densities are derived from the spatial distribution
where galaxies have been excluded.}

The luminosity from the dust is derived from the the luminosity to
richness scaling relation found in \cite{2008A&A...490..547G}
$L_\dust=10^{44.8}\left(\frac{N_{200}}{10}\right)^{0.8}$. We pic a high
richness $N_{200}=82$ cluster to normalize the luminosity since they
are less likely biased by chance coincidences. This richness roughly
correspond to $\mvir=6.0\times10^{14}\,\msun$
\cite{2010ApJ...713.1037H}. Assuming that the dust scales with halo
mass in the same way as the stars, we get
\begin{equation}
L_\stars(\mvir)=L_\stars(M_{200\rmn{av}})\,
\left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,.
\end{equation} 
The normalization constant for the dust in Eq.~(\ref{eq:E_SD}) can now
be determined:
\begin{equation}
 N_\dust(\mvir) =\,
\left(\frac{\mvir}{M_{200\rmn{av}}}\right)^{0.18}\,
\frac{\rvir}{\int_{\rvir} j(r) \,\dd V}\,.
\label{eq:N_dust}
\end{equation}

The spatial distribution of the SD energy density is an important quantity since
it impacts the steady state electron and positron spectra through cooling. A
higher density of SD in a cluster suppresses the spectra of the upscattering
particles. With the formalism presented above, we can now derive the energy
density from starlight and dust in a galaxy cluster through
\begin{eqnarray}
\label{eq:U_SD}
u_\sd(r) &=& \int \dd \eph \frac{\dd^2 N_\ph}{\dd \eph \dd V}\,\eph
=\int \dd \eph \frac{u_\sd(\eph, r)}{\eph}
\nonumber \\
&=&  j(r)  \int \dd \eph \sum_i 
N_i(\mvir) \frac{u_i^\gal(\eph)}{\eph}\,. \nonumber \\
\end{eqnarray}
In Fig.~\ref{fig:SD_Edens} we compare the energy densities from
different radiation fields in a galaxy cluster with the mass
$\mvir=4.0\times10^{13}\msun$. We use two different profiles for the
SD energy density, where the total profile includes the contribution
from the ICL, the BCG and all the galaxies, while the galaxies are
excluded in the smooth profile. We find that even for a cluster with a
relative small mass the energy density of the SD components dominates
over the CMB and the magnetic fields (with a central B field of 3~$\mu
G$) within about 10\% of $\rvir$. Outside this radius the CMB is
dominating the energy density of the cluster, hence the magnetic
fields are always subdominant in the cluster and can safely be removed
from cluster IC calculations for a reasonable central B-field and
spectral index. Note that in this work we keep the contribution
from B-fields to the total energy density for consistency.

@@

Our goal in this section is to derive a simple spatial model for the
distribution of SD in galaxy clusters. For this reason we use stacked
cluster observations by Sloan in the $r$ and $i$-band that trace the
stars. For simplicity we assume that the dust trace the stars in the
clusters [WHY IS THIS A GOOD APPROXIMATION]. The stacked surface
brightness profiles in \cite{2005MNRAS.358..949Z} are measured at
redshift $z \sim 0.25$ with an average mass of the clusters of
$4.0\times10^{13}\,\msun$. The profiles are build up out of three
components; diffuse intracluster light (ICL), galaxies, and the
brightest cluster galaxy (BCG) in the center of clusters. However, the
total volume overlap of the ISM to the cluster is very small compared
to the ICL- and BCG overlap with the cluster, thus the relative
contribution of the galaxies to the IC emission is suppressed. To
remove this bias we cut out the galaxies that have been smoothed over
the cluster in the stacked analysis. In Fig.~\ref{fig:SD_spatial} we
show the SDSS stacked brightness profiles as well as the fitted
profiles\footnote{The measured brightness is converted into units of
  $\rmn{erg}\,\rmn{s}^{-1}$ using \cite{2010...book}
  $S(\rmn{mag}\,''^{-2}) =
  \mathcal{M}_\odot+21.572-2.5\rmn{log}_{10}S(L_\odot\,\rmn{pc}^{-2})$,
  where the sun's absolute magnitude in the $r$-band is given by
  $\mathcal{M}_\odot=27.1$ \cite{1998gaas.book.....B} and the
  luminosity of the sun by $L_\odot=3.85\,10^{33}
  \rmn{erg}\,\rmn{s}^{-1}$.}, both scaled with the unitless $\rvir$
normalized area to resembele the expected luminosity at radius
$r$. Our benchmark spatial model is shown with the solid black line,
and include the contribution from the ICL and BCG.

Instead of modelling the surface brightness with a de Vaucouleur
profile with the addition of a power-law, we use a double beta profile
model for simplicity of deprojection given by:
\begin{equation}
\tilde{S}_\sd (r_\bot) = \frac{S_\sd (r_\bot)}{S_\rmn{SD}^\rmn{tot}(0)} = 
\sum_{i=1}^2 \,S_i\, 
\left[1 + \left( \frac{r_\bot}{r_{\mathrm{c}_i}}\right)^2\right]
^{-3\beta_i + 1/2}\,,
\label{double_beta}
\end{equation}
where we found the following best fitted normalized central brightness
($S_i$), core radius ($r_{\mathrm{c}_i}$), and slope ($\beta_i$) for
the total model:
\begin{align}
&\tilde{S}_1^\rmn{tot} = 1.0\,,
&&r_{\mathrm{c}_1}^\rmn{tot} = 1.8\,\rmn{kpc}\,,
&&&\beta_1^\rmn{tot} = 0.45\, \nonumber\\
&\tilde{S}_2^\rmn{tot} = 2.3\times10^{-3}\,,
&&r_{\mathrm{c}_2}^\rmn{tot} = 0.19\,\rvir\,,
&&&\beta_2^\rmn{tot} = 0.44\,.\nonumber\\
& && &&&
\label{fit_spatial_IR}
\end{align}
and for the smooth model
\begin{align}
&\tilde{S}_1^\rmn{sm}=0.47,\,
&&r_{\mathrm{c}_1}^\rmn{sm}=3.9\,\rmn{kpc}\,,
&&&\beta_1^\rmn{sm}=0.53 \,\nonumber\\
&\tilde{S}_2^\rmn{sm}=8.3\times10^{-4}\,,
&&r_{\mathrm{c}_2}^\rmn{sm}=0.19\,\rvir\,,
&&&\beta_2^\rmn{sm}=0.54\,.\nonumber\\
& && &&&
\label{fit_spatial_IR}
\end{align}
The 3D spatial profile is derived by deprojecting the surface
brightness in Eq.~(\ref{double_beta}) (see
e.g. \cite{2004A&A...413...17P} for details about the deprojection):
\begin{eqnarray}
  j(r)  = \sum_{i=1}^2 \frac{\tilde{S}_i}{2\pi\,r_{\mathrm{c}_i}}\,
  \frac{6 \beta_i - 1}{\left(1 + r^2/r^2_{\mathrm{c}_i}\right)^{3\beta_i}}\,
  \mathcal{B}\left(\frac{1}{2},3\beta_i\right)\,,
\end{eqnarray}
where $\mathcal{B}(a,b)$ denotes the beta-function
\cite{1965hmfw.book.....A}.
